\documentclass{cv}

\usepackage{minted}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}

\setname{Bernardo}{Meurer Costa}
\setposition{Software Engineer}
\setaddress{Brooklyn, New York}
\setmail{bernardo@meurer.org}
\setmobile{(805) 886--1045}
\setlinkedinaccount{https://www.linkedin.com/in/meurerbernardo/}
\setgithubaccount{https://github.com/lovesegfault}
\setthemecolor{teal}

\renewcommand{\baselinestretch}{0.9}

\begin{document}
\headerview%
\vspace{1ex}

\section{At a Glance}
\explanationdetail{
	\begin{itemize}
		\item 5+ years experience writing and deploying high-performance systems into production with Rust.

		\item Diverse breadth of experience, having worked on driving hardware devices, compilers, build systems, operating systems, and computer vision.

		\item Proven track record of debugging hard-to-reproduce hardware/software issues and communicating root causes and solutions effectively.

		\item Extensive experience porting large codebases to Rust and introducing Rust to teams.

		\item Strong communication skills, taking pride in speaking to others with candor and compassion.
	\end{itemize}
}

\section{Experience}
\datedexperience{AWS}{2022--Present}
\explanation{Senior Software Engineer  2023--Present}
\explanationdetail{
	\coloredbullet\ Lead developer for the BTLX (Builder Tools Language Experience) Rust team, in charge of the experience of over 4000 developers using Rust at AWS.\par
	\coloredbullet\ Sole team member to survive the wave of layoffs, taking on the load that was previously shared by a team of $\approx 5$ senior engineers.\par
	\coloredbullet\ Worked closely with the Rust compiler team, acting as the intermediary between Open Source and business needs of Rust at Amazon.\par
	\coloredbullet\ Drove various improvements to the Rust experience at Amazon, leading to many billions of dollars saved in engineering time and build infrastructure costs.\par
	\vspace*{1mm}
}
\explanation{Software Engineer  2022--2023}
\explanationdetail{
	\coloredbullet\ Worked on CargoBrazil, the integration between Cargo and
	Amazon's internal build system, Brazil.\par
	\coloredbullet\ Held the weekly Nix office hours, helping hundreds of
	developers become productive with Nix in the process.\par
	\vspace*{2.5mm}
}
\datedexperience{Google Quantum AI}{2021--2022}
\explanation{Software Engineer}
\explanationdetail{
	\coloredbullet\ Worked on QKernel, the operating system and control software
	for the quantum computer.\par
	\coloredbullet\ Worked on QCC, the quantum circuit compiler.\par
	\coloredbullet\ Lead the effort to port core components to Rust.\par
	\coloredbullet\ Participated in multiple complex incident responses, helping
	trace root causes and draft solutions.\par
	\coloredbullet\ Brought CI times from $\approx 40$ minutes to $\lesssim 10$
	minutes.\par
	\coloredbullet\ Implemented self-hosted GitHub Actions for a team of over
	100 engineers using GKE.\par
	\coloredbullet\ Automated the translation of SystemVerilog headers into
	Rust.\par
	\vspace*{2.5mm}
}
\datedexperience{Standard Cognition}{2018--2021}
\explanation{AI Systems Software Engineer}
\explanationdetail{
	\coloredbullet\ Initially worked on the camera and imaging stack, where I
	built the software that operates all cameras across their sites, managing
	upwards of 100Gb/s of image data with only on-site processing.\par
	\coloredbullet\ Transitioned into helping migrate data pipeline code from
	Python to Rust, eliminating years of technical debt.\par
	\coloredbullet\ Spearheaded a company-wide requirements gathering in order to
	understand our data needs. This evolved into a project to create better
	internal data engineering tools, which I worked on until 2020.\par
	\coloredbullet\ Helped review the acquisition of another company, where I was
	responsible for analyzing their stack and detecting possible issues during
	integration, as well as licensing issues.\par
	\coloredbullet\ Implemented a successful engineering-wide RFC process.\par
	\coloredbullet\ Debugged numerous hardware issues with cameras and worked
	with the vendor on developing and deploying fixes.\par
	\coloredbullet\ Helped bring Rust to the entire engineering team, taking us
	from my initial $\sim 2000$ LoC project to almost $60\,000$ lines of Rust
	company-wide.\par
	\vspace*{2.5mm}
	\newpage
}
\datedexperience{Hangar}{2015--2018}
\explanation{Founder}
\explanationdetail{
	\coloredbullet\ Co-founded Hangar, one of the first makerspaces in Brazil.\par
	\coloredbullet\ Helped grow the organization from 3 to over 30 members.\par
	\coloredbullet\ Held workshops on C, robotics, and Rust.\par
	\vspace*{2.5mm}
}
\datedexperience{Async Open Source}{2014--2016 Summers}
\explanation{Intern}
\explanationdetail{
	\coloredbullet\ Developed an application that helped customers easily migrate
	their databases to Postgres.\par
	\coloredbullet\ Migrated our application to mobile using Cordova.\par
	\coloredbullet\ Helped fix and triage many bugs in our usage of PyGTK.\par
	\vspace*{2.5mm}
}

\section{Skills}
\newcommand{\proglangs}{
	\createskill{Programming Languages}{
		\textbf{\emph{Experienced:}} \ \
		Rust \cpshalf%
		C  \cpshalf%
		Nix \cpshalf%
		Bash
		\ \
		\textbf{\emph{Familiar:}} \ \
		Python \cpshalf%
		C++ \cpshalf%
		VHDL \cpshalf%
		\LaTeX%
	}
}
\newcommand{\langs}{
	\createskill{Languages}{
		\textbf{\emph{Native:}} \ \
		Portuguese
		\ \
		\textbf{\emph{Fluent:}} \ \
		English
		\ \
		\textbf{\emph{Beginner:}} \ \
		Spanish \cpshalf%
		French
	}
}
\newcommand{\libraries}{
	\createskill{Libraries}{
		OpenCV \cpshalf%
		Gstreamer \cpshalf%
		FFmpeg \cpshalf%
		numpy \cpshalf%
		pandas \cpshalf%
		tokio \cpshalf%
		Aravis \cpshalf%
		nalgebra% \cpshalf%
	}
}
\newcommand{\tools}{
	\createskill{Tools}{
		Linux \cpshalf%
		Git \cpshalf%
		Nix \cpshalf%
		Cargo \cpshalf%
		Vim \cpshalf%
		Vivado \cpshalf%
		Meson \cpshalf%
		Portage
	}
}
\createskills{\proglangs,\langs,\libraries,\tools}

\section{Open-Source Projects}
\newcommand{\nixpkgs}{\href{https://github.com/NixOS/nixpkgs}{nixpkgs} --- Maintain binutils, firefox, thunderbird, beets, bindfs, and more}

\newcommand{\nix}{\href{https://github.com/lovesegfault/nix-config}{nix-config} --- My NixOS configuration spanning all my systems}

\newcommand{\genesis}{\href{https://github.com/lovesegfault/genesis}{genesis} --- Explorations into genetic algorithms}

\newcommand{\beautysh}{\href{https://github.com/lovesegfault/beautysh}{beautysh} --- Bash formatter}

\newcommand{\cachesize}{\href{https://github.com/lovesegfault/cache-size}{cache-size} --- Simple Rust crate to get the CPU cache sizes}

\newcommand{\daedalos}{\href{https://github.com/lovesegfault/daedalos}{daedalos} --- Rust kernel based on the osdev wiki}

\newcommand{\transcoders}{\href{https://github.com/lovesegfault/transcode-rs}{transcode-rs} --- Rust utility to discover, analyze, and transcode a video collection to AV1}

\newcommand{\hyperpixel}{\href{https://github.com/lovesegfault/hyperpixel-init}{hyperpixel-init} --- Configures and initializes the Hyperpixel 4 display, allowing you to use it without loading dtbs}

\newcommand{\cv}{\href{https://github.com/lovesegfault/cv}{cv} --- This very CV}

\newcommand{\listofprojects}{\nixpkgs,\nix,\genesis,\transcoders,\beautysh,\cachesize,\daedalos,\hyperpixel,\cv}
\createbullets{\listofprojects}

\section{Talks}
\newcommand{\rustlab}{
	RustLab 2019 --- Neobuffer: Safe, Lock Free, Cross-Process Channels in Rust \cpshalf%
	\href{https://www.youtube.com/watch?v=3NVev3FhGgk}{Recording} \cpshalf%
	\href{https://lovesegfault.com/slides/rustlab-2019.pdf}{Slides}
}

\newcommand{\listoftalks}{\rustlab}
\createbullets{\listoftalks}

\section{Education}
\datedexperience{Instituto Superior Técnico}{2016--2018}
\explanation{Coursework in Computer Engineering}
\explanationdetail{
	\hfill \break%
	\coloredbullet\ Digital Systems\par
	\coloredbullet\ Computer Architecture\par
	\coloredbullet\ Programming (C)\par
	\coloredbullet\ Linear Algebra\par
	\coloredbullet\ Applied Chemistry\par
	\coloredbullet\ Real Analysis\par
	\coloredbullet\ Multivariable Calculus\par
	\coloredbullet\ Mechanics \& Waves\par
	\coloredbullet\ Management of Engineering Projects\par
}

\section{Writing}
\newcommand{\euclidean}{\href{https://lovesegfault.com/posts/notes-on-euclidean-spaces/}{Notes on Euclidean Spaces}}

\newcommand{\pointers}{\href{https://lovesegfault.com/posts/c-arrays-are-not-pointers/}{C Arrays Are Not Pointers}}

\newcommand{\drm}{\href{https://lovesegfault.com/posts/drm-is-anti-copyright/}{DRM Is Anti-Copyright}}

\newcommand{\leibniz}{\href{https://lovesegfault.com/posts/on-leibniz-truth/}{On Leibniz's Truth}}

\newcommand{\factorial}{\href{https://oeis.org/A000142/a000142.pdf}{Swing, divide and conquer the factorial}}

\newcommand{\listofwriting}{\euclidean,\pointers,\drm,\leibniz,\factorial}
\createbullets{\listofwriting}

\section{Hobbies}
\newcommand{\printing} {3D printing}

\newcommand{\electronics} {Electronics (mostly radio and amplifier construction)}

\newcommand{\botany} {Botany / Taxonomy}

\newcommand{\listofhobbies}{\printing, \electronics, \botany}
\createbullets{\listofhobbies}

\section{Volunteering}
\newcommand{\taketothehills} {\href{https://taketothehills.net/}{Take to the Hills} --- Help mantain the Berkeley trails, cleaning them and keeping them filled with beautiful California native plants.}

\newcommand{\pecep} {\href{http://pecep.educacao.ws/}{PECEP} --- Taught mathematics to high school students from the Rocinha favela of Rio.}

\newcommand{\cs} {CS50 Brazil --- Was a TA during a recreation of the Harvard CS50 course in Rio de Janeiro.}

\newcommand{\listofvolunteering}{\taketothehills, \pecep, \cs}
\createbullets{\listofvolunteering}

\createfootnote%
\end{document}
